|

### 2022-12-12 r-report/Paper.Rmd
fixes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='hide', message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.height = 4, fig.width = 6)
options(knitr.kable.NA = '',knitr.table.format = "latex")
#knitr::read_chunk('r-report/Paper.R')
library(kableExtra)
```

```{r setup-ex}
source('r-imports/init.R')
source('r-analysis/meta.R')
theme_ghg = function(){ 
  theme_minimal() %+replace%
     theme(
       plot.title =element_blank(),
       plot.subtitle = element_blank()
    )
}
DIRECT_PLOTTING = F
```

@@

```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 1970
YEAR_U = 2020
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 201
COUNTRY = "China"
GAS = "GHG"

@@

```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r,fig.cap="Figure 6"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR = 1950
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Figure 7"}
source('r-imports/init.R')
source('r-analysis/meta.R')

YEAR = 1950
GAS = "GHG"
COUNTRY = "China"

@@

```{r,fig.cap="Figure 8"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 9"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

@@

```{r,fig.cap="Figure 10: Absolute GHG Emission - 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 11: Per Capita Emissions- 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 12: Absolute GDP p - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 13: GDP per Capita - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='hide', message=FALSE, warning=FALSE)
knitr::opts_chunk$set(fig.height = 4, fig.width = 6)
options(knitr.kable.NA = '',knitr.table.format = "latex")
knitr::read_chunk('r-report/Paper.R')
library(kableExtra)
```

```{r init}
```

@@

```{r init}
```
```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
YEAR_L = 1970
YEAR_U = 2020
GAS = "GHG"
COUNTRY = "China"

@@

```{r init}
```
```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

@@

```{r init}
```
```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
YEAR_L = 2000
YEAR_U = 201
COUNTRY = "China"
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
YEAR_L = 2000
YEAR_U = 2019
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="Figure 6"}
YEAR = 2019
GAS = "GHG"
COUNTRY = "China"

@@

```{r init}
```
```{r,fig.cap="Figure 7"}
YEAR = 2019
GAS = "GHG"
COUNTRY = "China"

@@

```{r init}
```
```{r,fig.cap="Figure 8"}
YEAR_L = 1970
YEAR_U = 2019
GAS = "GHG"
COUNTRY = "China"

source("r-analysis/data_sector_incomelevel.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_facet_incomelevels_sectors_emissions.R", local = TRUE, print.eval = TRUE)

@@

```{r init}
```
```{r,fig.cap="Figure 9"}
YEAR_L = 1970
YEAR_U = 2019
FYEAR_L = c(2025,2030,2030,2035,2040)
FYEAR_U = c(2060,2060,2055,2065,2065)
FYEAR_US = 2050
FYEAR_EU = 2050
GAS = "GHG"

source("r-analysis/forecast.R", local = TRUE, print.eval = TRUE)
source("r-plots/plot_forecast.R", local = TRUE, print.eval = TRUE)

```{r,fig.cap="Figure 10"}
source("r-plots/plot_forecast_delta.R", local = TRUE, print.eval = TRUE)

```{r init}
```
```{r,fig.cap="Figure 11"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r,fig.cap="Figure 12"}
source("r-plots/plot_cumulative_china_2040.R", local = TRUE, print.eval = TRUE)

@@

```{r init}
```
```{r,fig.cap="Figure 10: Absolute GHG Emission - 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="Figure 11: Per Capita Emissions- 2019 | Top Emittters, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="Figure 12: Absolute GDP p - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

@@

```{r init}
```
```{r,fig.cap="Figure 13: GDP per Capita - 2019 | Highes GDP Countries, China, US, EU-27 and reference for GDP, Emissions and Population"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"
